---
title: "ECON 121 FA23 Problem Set 1"
author: "Your name"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # sets the code chunk format
rm(list = ls()) # clears the environment
```

## Question 1

Verbal: list group members.

\newpage

## Question 2

Code: Load packages and dataset, summarize the data.

Verbal: Interpret the summary statistics.

```{r message=FALSE, warning=FALSE}
# The PDF will show the code you write here but not the output.
# Load packages and dataset here.
library(tidyverse)
library(fixest)
data = read.csv(url("https://github.com/tvogl/econ121/raw/main/data/ssa_names.csv"))

```

```{r echo=TRUE}
# The PDF will show the code AND output here.
# Summarize the data here.
summary(data)
```

\newpage

## Question 3

Code: Find the all time most common boy and girl names.

Verbal: Interpret your results.

```{r echo=TRUE}
# All question 3 code here
agg_data <- aggregate(frequency ~ name + sex, data, sum)

# Find the most popular boy and girl names
most_popular_boy <- agg_data[agg_data$sex == 'M',][order(-agg_data[agg_data$sex == 'M',]$frequency),][1,]
most_popular_girl <- agg_data[agg_data$sex == 'F',][order(-agg_data[agg_data$sex == 'F',]$frequency),][1,]

cat(paste("The most popular boy name is", most_popular_boy$name, "with", most_popular_boy$frequency, "babies named between 1940 and 2022.\n"))
cat(paste("The most popular girl name is", most_popular_girl$name, "with", most_popular_girl$frequency, "babies named between 1940 and 2022.\n"))
```

\newpage

## Question 4

Code: Plot time trends in the number of unique names by sex

Verbal: Interpret your results.

```{r echo=TRUE}
# All question 4 code here
unique_names_count <- aggregate(name ~ year + sex, data, function(x) length(unique(x)))

# Plot the trends
ggplot(unique_names_count, aes(x=year, y=name, color=sex)) +
  geom_line() +
  labs(title="Time Trends in Number of Unique Names by Sex",
       x="Year",
       y="Number of Unique Names",
       color="Sex") +
  theme_minimal()
```

\newpage

## Question 5

Code: Plot time trends in the number of unique names relative to the number of 
babies by sex.

Verbal: Interpret your results.

```{r echo=TRUE}
# All question 5 code here

```

\newpage

## Question 6

Verbal: Which names and why?

\newpage

## Question 7

Code: Find all-time frequency of your names and compare with all-time most
popular names.

Verbal: Interpret your results.

```{r echo=TRUE}
# All question 7 code here

```

\newpage

## Question 8

Code: Graph the annual frequencies of your chosen name(s) over time.

Verbal: Interpret your results.

```{r echo=TRUE}
# All question 8 code here

```

